---
title: "Bayesian Inference"
author: ''
date: '2020-04-13'
slug: bayesian_Inference
tags: []
categories: bayesian
---


## 问题描述
 
 15次独立的抛硬币试验，正面的概率为$p$,未知量。利用贝叶斯定理做一些推断
 将 $X_1,...,X_n$ 代表试验， ($X_i = 1$ 表示正面, 0 反面). 贝叶斯定理说的是:

$$\pi( p \, | \, X_1,...,X_n) = \frac{L( X_1,...,X_n \, | \, p)\pi(p)}{\pi(X_1,...,X_n)},$$ 

其中 $\pi( p \, | \, X_1,...,X_n)$ 为 $p$ 的先验概率分布, $L( X_1,...,X_n \, | \, p)$ 为似然函数, $\pi(p)$ 关于 $p$的先验概率分布,  $\pi(X_1,...,X_n)$ 为“证据” (可以利用全概率公式计算). 

## First
 Descretize the parameter space by making a grid of $m = 100$ values for $p$ between 0 and 1. Then, create a vector of prior probabilities that assigns equally likely probabilities to each value of $p$.
 
```{r}
library(tidyverse)
library(ggplot2)
p_vals <- seq(0,1,length.out = 100) 
p_prior <- 1/100
```
## Second
We flip the coin 15 times, and count 4 heads. Calculate the probability of getting 4 heads in 15 tosses under each value of $p$  given above. These are values of the likelihood function.
```{r}
likehood_vals <- dbinom(x = 4,size = 15,prob = p_vals)
```

## Third


 Use Bayes' theorem and the information from previous parts to calculate the posterior distribution for each of the 100 values of $p$. Plot and describe the posterior distribution.
```{r}
marg_likehood <- sum(likehood_vals * p_prior)
p_posterior <- (likehood_vals*p_prior)/marg_likehood
df_bayes <- tibble(
p_vals,
likehood_vals,
p_prior,
p_posterior
)
ggplot(df_bayes,aes(x = p_vals, y = p_posterior)) +
    geom_point() +
    geom_segment(aes(x = p_vals, xend = p_vals, y = p_posterior, yend = 0)) +
    xlab(expression(p)) +
    ylab(expression(paste("P(", p, "|D)"))) +
    ggtitle("Posterior Distribution")
```
 
 